### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@63aca186d2ffaa114ff93cc23b677f40d26ffd9a 🚀

The dataset used for numerical experiments is composed of 20000 such
\((\xi, \nu)\) pairs, on which four models are trained: a decision tree
regressor, a boosted regression tree, a ridge regressor, and a random
forest regressor. All models were taken from the \texttt{MLJ.jl} package
(Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7 (Bezanson et
al., 2017). The complete code to run the simulations is given as an
appendix. \#\# Effect of training set on performance

>>>>

The dataset used for numerical experiments is composed of 20000 such
\((\xi, \nu)\) pairs, on which four learners are trained: a decision
tree regressor, a boosted regression tree, a ridge regressor, and a
random forest regressor. All models were taken from the \texttt{MLJ.jl}
package (Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7
(Bezanson et al., 2017). In order to pick the best adjacency matrix for
a given learner, we performed a thresholding approach using 500 steps on
predictions from the testing set, and picking the threshold that
maximized Youden's informedness, which is usually the optimized target
for imbalanced classification. During the thresholding step, we measured
the area under the receiving-operator characteristic (ROC-AUC) and
precision-recall (PR-AUC) curves, as measures of overall performance
over the range of returned values. We report the ROC-AUC and PR-AUC, as
well as a suite of other measures as introduced in the next section, for
the best threshold. The ensemble model was generated by summing the
predictions of all component models on the testing set (ranged in
\([0,1]\)), then put through the same thresholding process. The complete
code to run the simulations is given as an appendix.

After the simulations were completed, we removed all runs (\emph{i.e.}
pairs of \(\xi\) and \(\nu\)) for which at least one of the following
conditions was met: the accuracy was 0, the true positive or true
negative rates were 0, the connectance was larger than 0.2. This removes
both the obviously failed model runs, and the networks that are more
densely connected compared to the connectance of empirical food webs
(and are therefore less difficult to predict, being less imbalanced).

\hypertarget{effect-of-training-set-on-performance}{%
\subsection{Effect of training set on
performance}\label{effect-of-training-set-on-performance}}
